Challenging Fuel Cycle Modeling Assumptions: Facility and Time Step Discretization Effects

### 2016-04-22 paper.tex
add hack to get line numbers in diff
remove watermark and add submittephone and institute address

\usepackage[printwatermark]{xwatermark}
\usepackage{xcolor}
\newwatermark[allpages,color=black!5,angle=45,scale=6,xpos=-40,ypos=40]{DRAFT}

@@

\institute{University of Wisconsin - Madison, Department of Nuclear Engineering and Engineering Physics, Madison, WI 53706}
\submitter{Robert W. Carlsen}
\submitteraddress{229 N Midvale Blvd Apt 1, Madison, WI 53705}
\submitteremail{rwcarlsen@gmail.com}

@@

\usepackage{graphicx}
\usepackage{placeins}
\usepackage{tabularx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{cite} % order citations correctly
\usepackage{float} % used to help position figures with the H modifier

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{ans}
\bibliography{refs}
\end{document}

>>>>

@@

\institute{University of Wisconsin - Madison, Department of Nuclear Engineering and Engineering Physics}
\instituteaddress{1415 Engineering Drive, Madison, WI 53706}

\submitter{Robert W. Carlsen}
\submitteraddress{229 N Midvale Blvd Apt 1, Madison, WI 53705}
\submitteremail{rwcarlsen@gmail.com}
\submitterphone{208/705-0291}

@@

\usepackage{graphicx}
\usepackage{placeins}
\usepackage{tabularx}
\usepackage{booktabs} % nice rules for tables
\usepackage{microtype} % if using PDF
\usepackage{xspace}
\usepackage{hyperref}
\usepackage{caption}
\usepackage{cite} % order citations correctly
\usepackage{float} % used to help position figures with the H modifier
\usepackage[modulo]{lineno}

@@

%lineno\begin{linenumbers}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bibliographystyle{ans}
\bibliography{refs}

%lineno\end{linenumbers}

\end{document}
